Supplemental Information: Continuous developmental changes in word recognition support language learning across early childhood

### 2025-10-13 paper/supplemental_information.Rmd
fix a couple typos and allow for "first time" eval

```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE)
library(here)
source(here("helper","common.R"))
#library(kableExtra)
library(papaja)
```

```{r, echo=FALSE, cache=TRUE, message=FALSE, warning=FALSE, include=F}
paper <- suppressMessages(knitr::purl(here("paper","paper.Rmd"), documentation = 0))
suppressMessages(source(paper))
```

@@

```{r, eval=F}
library(brms)
library(tidybayes)

@@

fitted_vals <- fitted(mod_brms, newdata = new_data, re_formula = NA, summary = TRUE)

>>>>

```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE)
library(here)
source(here("helper","common.R"))
#library(kableExtra)
library(papaja)

#set to TRUE to fit the Bayesian models
FIT_BAYES = FALSE
```

```{r, echo=FALSE, cache=FALSE, message=FALSE, warning=FALSE, include=F}
paper <- suppressMessages(knitr::purl(here("paper","paper.Rmd"), documentation = 0))
suppressMessages(source(paper))
```

@@

```{r, eval=FIT_BAYES}
library(brms)
library(tidybayes)

@@

fitted_vals <- fitted(resid_mod_brms, newdata = new_data_resid, re_formula = NA, summary = TRUE)
